NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-03-31 paper/appendix_modelDescription.tex
add open source comment add title to the appendix
update supplementray material

%% Paper title.
\title{
Supplementary Materials
%Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
}
\vgtcinsertpkg

@@

\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
from visPackage import *
from modelInterface import *
from sentenceGenerator import *

@@

#define visualization components
visLayout = {
    "column":[{"row":["Selector", 
                      "Sentence", 
                      "Pipeline"]},
            {"row":["AttentionGraph", 
                    "AttentionMatrix", 
                    "Prediction"]}]
    }

#create vis interface
vis = textEntailVisModule(visLayout)

>>>>

%% Paper title.
\title{
NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials
%Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
}
\vgtcinsertpkg

@@

\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
from nlize import *
from modelInterface import *
from sentenceGenerator import *

@@

#define visualization components
visLayout = {
    "column":[{"row":["Summary", 
                      "Sentence", 
                      "Pipeline"]},
            {"row":["AttentionGraph", 
                    "AttentionMatrix", 
                    "Prediction"]}]
    }

#create vis interface
vis = nlizeModule(visLayout)

### 2018-03-31 paper/task.tex
update supplementray material

\item \textbf{T3}: When the predicted label is incorrect, what does it take to fix the model? What is the effect of updating different stages of the model?

>>>>

\item \textbf{T3}: When the predicted label is wrong, how can we update the model to correct the prediction? What is the effect of updating different parts of the model?
